Exoplanet population inference and the abundance \\ of Earth analogs from noisy, incomplete catalogs

### 2014-08-11 document/ms.tex
acking the referee
samsi ack

\acknowledgments
We would like to thank Erik Petigura (Berkeley) for freely sharing his data
and code.
It is a pleasure to thank
Ruth Angus (Oxford),
Tom Barclay (NASA Ames),
Jo Bovy (IAS),
Eric Ford (PSU), and
Ben Montet (Caltech/Harvard)
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), NASA
(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
This research builds on ideas generated at a three-week workshop on ``Modern
Statistical and Computational Methods for Analysis of Kepler Data'' at SAMSI
in 2013 June.
This research made use of the NASA \project{Astrophysics Data System}.

>>>>

\acknowledgments
We would like to thank Erik Petigura (Berkeley) for freely sharing his data
and code.
It is a pleasure to thank
Ruth Angus (Oxford),
Tom Barclay (NASA Ames),
Jo Bovy (IAS),
Eric Ford (PSU), and
Ben Montet (Caltech/Harvard)
for helpful contributions to the ideas and code presented here.
We would also like to acknowlege the anonymous referee for suggestions that
substantially improved the paper.
This project was partially supported by the NSF (grant AST-0908357), NASA
(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
This research builds on ideas generated at a three-week workshop supported by
NSF Grant DMS-1127914 to the Statistical and Applied Mathematical Sciences
Institute.
This research made use of the NASA \project{Astrophysics Data System}.
